Computing exact restricted isometry constants via\\ mixed integer semidefinite programming

### 2015-01-02 RIP-MISDP-Paper/Paper_v1.tex
trace and rank in normal font
use \abs and \ones

\newcommand{\suchthat}{\,:\,}
\newcommand{\abs}[1]{\lvert{#1}\rvert}
\newcommand{\card}[1]{\lvert{#1}\rvert}
\newcommand{\define}{\coloneqq}
\newcommand{\enifed}{\eqqcolon}
\newcommand{\norm}[1]{\lVert{#1}\rVert}
\newcommand{\Norm}[2]{\lVert{#1}\rVert_{#2}}
\newcommand{\skal}[2]{\langle{#1},{#2}\rangle}
\newcommand{\order}[1]{O\left({#1}\right)}
\newcommand{\T}{^{\top}}
\newcommand{\Tr}{\textbf{Tr}}
\newcommand{\Rk}{\textbf{Rk}}

@@

In this section we will discuss two known SDP relaxations to compute an upper bound on the restricted isometry constant $\delta_k$ in (\ref{rip}), as they have some ideas in common with the mixed integer semidefinite program we want to 
propose and will also be checked against in the section on numerical results. The idea of these two relaxations as well as the MISDP in the next section is that the optimal constant $\alpha_k^2$ in (\ref{asymRIP}) can be computed
with the non-convex quadratic optimization problem
\begin{align}\label{QP}
 \min \quad & \Norm{Ax}{2}^2 \nonumber \\
 \text{s.t.} \quad & \Norm{x}{2}^2 = 1 \tag{QP} \\
 & \Norm{x}{0} \leq k. \nonumber
\end{align}
The corresponding maximization problem can be solved to compute $\beta_k^2$. In \cite{Asp07} the non-convex quadratic equality constraint $\Norm{x}{2}^2 = 1$ is tackled by the technique of semidefinite lifting first introduced in \cite{GW95} 
for the max-cut problem. The idea is to use a new matrix variable $X=xx\T$ for the quadratic terms, where the condition $X=xx\T$ is then enforced by the equivalent constraints $X \succeq 0$ and $\Rk(X) = 1$, where 
$X \succeq 0$ means that $X$ is symmetric and positive semidefinite. In the next step the non-convex rank constraint is then relaxed and the inequality $\Norm{x}{0} \leq k$ is substituted by the coarser constraint $1\T|X|1 \leq k$ to form
the relaxation
\begin{align}\label{Asp07}
 \min \quad & \Tr(A\T A X) \nonumber \\
 \text{s.t.} \quad & \Tr(X) = 1 \nonumber \\
 & \ones\T|X|\ones \leq k \tag{A1} \\
 & X \succeq 0. \nonumber
\end{align}

>>>>

\newcommand{\suchthat}{\,:\,}
\newcommand{\abs}[1]{\lvert{#1}\rvert}
\newcommand{\card}[1]{\lvert{#1}\rvert}
\newcommand{\define}{\coloneqq}
\newcommand{\enifed}{\eqqcolon}
\newcommand{\norm}[1]{\lVert{#1}\rVert}
\newcommand{\Norm}[2]{\lVert{#1}\rVert_{#2}}
\newcommand{\skal}[2]{\langle{#1},{#2}\rangle}
\newcommand{\order}[1]{O\left({#1}\right)}
\newcommand{\T}{^{\top}}
\newcommand{\Tr}{\text{Tr}}
\newcommand{\Rk}{\text{Rk}}

@@

In this section we will discuss two known SDP relaxations to compute an upper bound on the restricted isometry constant $\delta_k$ in (\ref{rip}), as they have some ideas in common with the mixed integer semidefinite program we want to 
propose and will also be checked against in the section on numerical results. The idea of these two relaxations as well as the MISDP in the next section is that the optimal constant $\alpha_k^2$ in (\ref{asymRIP}) can be computed
with the non-convex quadratic optimization problem
\begin{align}\label{QP}
 \min \quad & \Norm{Ax}{2}^2 \nonumber \\
 \text{s.t.} \quad & \Norm{x}{2}^2 = 1 \tag{QP} \\
 & \Norm{x}{0} \leq k. \nonumber
\end{align}
The corresponding maximization problem can be solved to compute $\beta_k^2$. In \cite{Asp07} the non-convex quadratic equality constraint $\Norm{x}{2}^2 = 1$ is tackled by the technique of semidefinite lifting first introduced in \cite{GW95} 
for the max-cut problem. The idea is to use a new matrix variable $X=xx\T$ for the quadratic terms, where the condition $X=xx\T$ is then enforced by the equivalent constraints $X \succeq 0$ and $\Rk(X) = 1$, where 
$X \succeq 0$ means that $X$ is symmetric and positive semidefinite. In the
next step the non-convex rank constraint is then relaxed and the inequality
$\Norm{x}{0} \leq k$ is substituted by the coarser constraint $\ones\T
\abs{X} \ones \leq k$ to form
the relaxation
\begin{align}\label{Asp07}
 \min \quad & \Tr(A\T A X) \nonumber \\
 \text{s.t.} \quad & \Tr(X) = 1 \nonumber \\
 & \ones\T \abs{X} \ones \leq k \tag{A1} \\
 & X \succeq 0. \nonumber
\end{align}
